Of judges, aliens and total preorders

### 2021-02-12 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: some more slides + brought back itemize dots

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{pgfpages}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{stmaryrd}

@@

% TODO theorems/definitions etc should be numbered

% TODO itemize dots seem to be lost

@@

\begin{frame}{Enriching Epistemic States}
    \note{
        \begin{itemize}
            \item W+-
        \end{itemize}
    }
\end{frame}

@@

\begin{frame}{Courtroom example: $\leq$-faithful tpo}
    \note{
        \begin{itemize}
            \item example for courtroom
        \end{itemize}
    }
\end{frame}

@@

\begin{frame}{BM tpo-revision operator}
    \note{
        \begin{itemize}
            \item definition
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom example: Revision}
    \note{
        \begin{itemize}
            \item example 7, math
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom example: Revision Visualised}
    \note{
        \begin{itemize}
            \item example 7, figure 4
        \end{itemize}
    }
\end{frame}

>>>>

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{pgfpages}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{stmaryrd}

\usepackage{enumitem}
\setitemize{label=\usebeamerfont*{itemize item}
  \usebeamercolor[fg]{itemize item}
  \usebeamertemplate{itemize item}}

@@

@@

\begin{frame}{Enriching Epistemic States}
    \begin{itemize}
        \item $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$
        \item $w \in \modelsOf{\alpha}$ / $w \in \modelsOf{\neg\alpha}$
        \item $(w^{+}, w^{-})$
    \end{itemize}
    \note{
        \begin{itemize}
            \item W+-
        \end{itemize}
    }
\end{frame}

@@

\begin{frame}[fragile]{Courtroom example: $\leq$-faithful tpo}
   \begin{figure}[H]
            \centering
            \begin{tikzpicture}[scale=1]
                \begin{axis}[
                        xticklabels={},
                        yticklabels={},
                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
                        ytick style={draw=none},
                        xtick style={draw=none},
                        axis line style={draw=none}
                ]
                \addplot[
                    scatter,
                    scatter src=explicit symbolic,
                    mark size=3,
                    scatter/classes={
                        empty={mark=*, fill=white},
                        filled={mark=*, fill=black}
                    },
                    nodes near coords*={\Label},
                    visualization depends on={value \thisrow{label} \as \Label}
                ]
                table [meta=class] {
                        x y class label

                        1 8 empty \empty
                        3 8 empty

                        1 7 empty 
                        3 7 empty

                        2 6 empty 
                        4 6 empty

                        2 5 empty 
                        4 5 empty

                        5 4 empty 
                        7 4 empty

                        5 3 empty 
                        7 3 empty

                        6 2 empty 
                        8 2 empty

                        6 1 empty 
                        8 1 empty
                        };
                \end{axis}
            \end{tikzpicture}
            \caption{Representation of $\preceq$ over $W^{\pm}$ for the courtroom example \ref{example:example-introduction}}
            \label{fig:example-tpo-initial}
    \end{figure}

    \note{
        \begin{itemize}
            \item example for courtroom
        \end{itemize}
    }
\end{frame}

@@

\begin{frame}{BM tpo-revision operator}
    \begin{definition}[Revision operator $\ast_{\preceq}$ for $\leq$ generated by $\preceq$ \cite{Booth2011}]
        \label{definition:revision-operator}
        For each $\leq$-faithful tpo $\preceq$ over $W^{\pm}$, refer to $\ast_{\preceq}$ as the revision operator for $\leq$ generated by $\preceq$ defined by:

        Set for any $\alpha \in L$ and $x \in W$:
        \begin{equation*}
            r_{\alpha}(x) = \left\{
                        \begin{array}{ll}
                          x^{+} \textrm{ if } x \in \modelsOf{\alpha}\\
                          x^{-} \textrm{ if } x \in \modelsOf{\neg\alpha}
                        \end{array}
                      \right.
        \end{equation*}

        The revised tpo $\leq_{\alpha}^{\ast}$ is defined by setting, for each $x, y \in W$,

        \begin{equation*}
            x \leq_{\alpha}^{\ast} y \textrm{ iff } r_{\alpha}(x) \preceq r_{\alpha}(y)
        \end{equation*}
    \end{definition}

    \note{
        \begin{itemize}
            \item definition
        \end{itemize}
    }\include{figures/example-visualisation-scatterplot}
\end{frame}

\begin{frame}[fragile]{Courtroom example: Revision Visualised}

    \begin{figure}[H]
            \centering
            \begin{tikzpicture}[scale=1]
                \begin{axis}[
                        xticklabels={},
                        yticklabels={},
                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
                        ytick style={draw=none},
                        xtick style={draw=none},
                        axis line style={draw=none}
                ]
                \addplot[
                    scatter,
                    scatter src=explicit symbolic,
                    mark size=3,
                    scatter/classes={
                        empty={mark=*, fill=white},
                        filled={mark=*, fill=black}
                    },
                    nodes near coords*={\Label},
                    visualization depends on={value \thisrow{label} \as \Label}
                ]
                table [meta=class] {
                        x y class label

                        1 8 empty \empty
                        3 8 filled

                        1 7 filled 
                        3 7 empty

                        2 6 empty 
                        4 6 filled

                        2 5 filled 
                        4 5 empty

                        5 4 empty 
                        7 4 filled

                        5 3 filled 
                        7 3 empty

                        6 2 empty 
                        8 2 filled

                        6 1 filled 
                        8 1 empty
                        };
                \end{axis}
            \end{tikzpicture}
            \caption{Associating positive and negative representations of worlds after receiving evidence $\alpha=p$}
            \label{fig:example-tpo-revised}
    \end{figure}

    \note{
        \begin{itemize}
            \item example 7, figure 4
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom example: Revision}

    \begin{itemize}
        \item for $010, 110 \in W$, $010 \leq 110$ before, revise by $\alpha = p$
    \end{itemize}

    \begin{equation*}
        010 \in \modelsOf{\neg\alpha} \textrm{ : } r_{\alpha}(010) = 010^{-}
    \end{equation*}
    \begin{equation*}
        110 \in \modelsOf{\alpha} \textrm{ : } r_{\alpha}(110) = 110^{+}
    \end{equation*}

    \begin{itemize}
        \item $110^{+} \prec 010^{-}$ is true, set $110 <_{\alpha}^{\ast} 010$
        \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
        \item $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
        \item $\leq_{\alpha}^{\ast}$ as representation of the conditional beliefs
        \begin{itemize}
            \item before $010 \leq 110$: "Both suspects being the murderer is less plausible than Mary being the murderer"
            \item now $110 <_{\alpha}^{\ast} 010$: "Only Mary being the murderer less plausible than both conspiring".
        \end{itemize}
    \end{itemize}

    \note{
        \begin{itemize}
            \item example 7, math
        \end{itemize}
    }
\end{frame}
